conmat: generate synthetic contact matrices for a given age-stratified population

### 2024-07-16 paper/paper.Rmd
Updated "model interface" section

- Input: age and population data, and Output: synthetic contact matrix
- Create next generation matrices (NGMs)
- Apply vaccination reduction to NGMs
- Use NGMs in disease modelling
- Provide tidy Australian survey data from the Australian Bureau of Statistics for use.

@@

[ #NOTE revised text of above paragraph ]
`conmat` was built to predict at four settings: work, school, home, and other. 
The model fitted is a Poisson generalised additive model (GAM) which predicts the count of contacts, with an offset for the log of participants. The model has six (?)covariates/terms to explain six key features of the relationship between ages, and two optional terms for attendance at school or work. The two optional terms are included depending on which setting the model is fitted for. There are four resulting models, with one model fitted for each setting.

@@

The six key features of the relationship are shown in the figure below.

@@

Each cell in the resulting contact matrix, indexed *i*, *j*, is the predicted number of people in age group *j* that a single individual in age group *i* will have contact with per day. If you sum across all the *j* age groups for each *i* age group, you get the predicted total number of contacts per day for each individual of age group *i*. [ #TODO expected, predicted, or average?]

[ #TODO notes-to-self: the model structure wasn't generated through any particularly robust process, it was just coming up with structures that looked mildly appropriate for our use case.

@@

We provide multiple levels for the user to interact with for model fitting, further detail can be seen at: https://idem-lab.github.io/conmat/dev/

* `fit_single_contact_model()`
    * Using contact survey data to fit a GAM model, adding provided target population information to provide population size information. Recommended for when you want to fit to just a single setting, for which you might want to provide your own contact survey data.

@@

    * This takes a fitted model from `fit_single_contact_model`, and then predicts to a provided population

* `fit_setting_contacts()`
    * Fits the `fit_single_contact_model()` to each setting. Recommended for when you have multiple settings to fit. Returns a list of fitted models.

* `predict_setting_contacts()`
    * Takes a list of fitted models from `fit_setting_contacts()` and predicts to a given population for each setting.

@@

>>>>

The `conmat` package was developed to fill the specific need of creating synthetic contact matrices for local government areas in Australia. This package is used for [ #TODO what work, specifically? Health? Provide example. Or is *this* package commissioned by the Aus govt? ] work commissioned by the Australian government.
We developed methods and software to facilitate the following tasks.

- Generate, as output, synthetic contact matrices from age-stratfied population data.
- Create next generation matrices (NGMs).
- Apply vaccination reduction to NGMs.
- Use NGMs in disease modelling.
- Provide tidied population data from the Australian Bureau of Statistics.

@@

`conmat` was built to predict at four settings: work, school, home, and other. 
The model fitted is a Poisson generalised additive model (GAM) which predicts the count of contacts, with an offset for the log of participants. The model has six (?)covariates/terms to explain six key features of the relationship between ages, and two optional terms for attendance at school or work. The two optional terms are included depending on which setting the model is fitted for. There are four resulting models, with one model fitted for each setting.

@@

The six key features of the relationship between the age groups, represented by the six terms, are displayed in the figure below.

@@

Each cell in the resulting contact matrix, indexed *i*, *j*, is the predicted number of people in age group *j* that a single individual in age group *i* will have contact with per day. If you sum across all the *j* age groups for each *i* age group, you get the predicted total number of contacts per day for each individual of age group *i*. [ #TODO expected, predicted, or average? ]

[ #TODO notes-to-self: the model structure wasn't generated through any particularly robust process, it was just coming up with structures that looked mildly appropriate for our use case. ]

@@

We provide functions for model fitting at various use cases. Further detail for each of the following functions can be seen at: https://idem-lab.github.io/conmat/dev/

* `fit_single_contact_model()`
    * Fits a generalised additive model (GAM) using contact survey data and population size information. This function is recommended for when you want to fit a model to only one setting, for which you might want to provide your own contact survey data.

@@

    * This takes a fitted model from `fit_single_contact_model()` and predicts [ #TODO what is predicted? ] to a provided (?) population structure.

* `fit_setting_contacts()`
    * Fits the `fit_single_contact_model()` to each setting. This function is useful for when you have multiple settings to fit. Returns a list of fitted models.

* `predict_setting_contacts()`
    * Takes a list of fitted models from `fit_setting_contacts()` and predicts [ #TODO what is predicted? ] to a given population for each setting.

@@

[ #TODO for the above it's good to explain what exactly is predicted. Otherwise it's confusing for the user to understand what each of the model outputs? ]
